---
title: "coding"
author: "Jinyu"
date: "2023-01-18"
output: html_document
##Group members：OJHA Anushree，Caroline JOHNSON，Jinyu LIN
##Question：Bike sharing
##Database Source：https://www.kaggle.com/competitions/bike-sharing-demand/overview
##Our team division:
  
##Part 1: Introduction
        Presentation and description of the problem  -- By OJHA Anushree 


##Part 2: Presentation of the data
        Exploratory data analysis
        Visualization of the data --By Jinyu LIN

##Part 3: Conclusion  --By Caroline JOHNSON
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
Sys.setlocale("LC_TIME", "English")
```

# Preparation

```{r message=FALSE}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(plotly)
```

```{r}
data = read_csv("train.csv")
```

# Most frequently used days

```{r}
data %>%
  mutate(weekday = weekdays(datetime)) %>%
  group_by(weekday) %>%
  summarise(number = sum(count)) %>%
  ggplot(aes(x = reorder(weekday, number), y = number)) +
  geom_col() +
  labs(x = "Weekdays", y = "Counts") +
  scale_y_continuous(labels = scales::comma) +
  theme_bw()
```

It seems that there is no difference.

# The relationship between different seasons and the number of car rentals

```{r}
p <- data %>%
  group_by(season) %>%
  summarise(number = sum(count)) %>%
  ggplot(aes(x = season, y = number)) +
  geom_point() +
  geom_line() +
  labs(x = "Season", y = "Counts") +
  scale_y_continuous(labels = scales::comma) +
  theme_bw()
ggplotly(p)
```

# Average number of rentals per day in 24 hours per season

```{r}
p1 = data %>% separate(datetime, into = c("data", "time"), sep = " ") %>% 
  group_by(season, time) %>% 
  summarise(mean = mean(count)) %>% 
  mutate(Time = as.numeric(as.factor(time))) %>% 
  ggplot(aes(Time, mean)) + 
  geom_line(aes(color = factor(season), group = season)) + 
  geom_point(aes(color = factor(season))) +
  scale_x_continuous(limits = c(1,24), breaks = seq(0,24,2)) + 
  labs(y = "Count", x = "Time", color = "Season")
ggplotly(p1)
```



When temp is less than 35 Celsius, the correlation is positive. But if the temperature is too high, people don't like to ride bikes.

# How many people are renting a car per hour?

```{r}
p3 <- data %>%
  mutate(hour = hour(datetime)) %>%
  ggplot(aes(x = factor(hour), y = count)) +
  geom_boxplot() +
  labs(x = "Hours", y = "Counts") +
  theme_bw()
ggplotly(p3)
```

# The relationship between temperature and rental volume

```{r}
p2 <- ggplot(data = data, aes(x = temp, y = count)) +
  geom_point() +
  geom_smooth() +
  theme_bw()
ggplotly(p2)
```

# The difference in count at 0-24

```{r}
p4 <- data %>%
  mutate(hour = hour(datetime)) %>%
  group_by(hour) %>%
  summarise(number = sum(count)) %>%
  ggplot(aes(x = hour, y = number)) +
  geom_col() +
  labs(x = "Hours", y = "Counts") +
  theme_bw()
ggplotly(p4)
```

It is clear that around 9 a.m. and 6 p.m. is the peak period for rentals, which also coincides with people's commuting times.

# Correlation analysis

```{r}
library(ggcorrplot)
ggcorrplot(cor(data[, -1]),hc.order=TRUE,
           outline.color="white",colors = c("#6D9EC1", "white", "#E46726"), lab = TRUE)
```

It can be seen temp is positively correlated with count, humidity and weather are negatively correlated with count.The number of people renting a car in cold weather will decrease, and in wet and rainy weather, most people are reluctant to rent a car.

